Group assignment

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

## 1.3 Descriptive statistics
## • Summary for the main variables in the transformed dataset
## *Numeric variables*
```{r echo=FALSE}
datasummary(distance + starrating + actualrating + trueprice ~ Mean + Min + Max + SD, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
### There are prominent outliers for *distance* and *true price* variables, therefore, the dataset was transformed, setting the maximum values at the 99% percentile (35 miles and 600 EUR respectively).

@@

## 1.4.2 Country

## 1.4.3 Distance

@@

>>>>

## 1.3 Descriptive statistics
## Summary od the main variables in the transformed dataset
## *Numeric variables*
```{r echo=FALSE}
datasummary(distance + starrating + actualrating + trueprice ~ Mean + Min + Max + SD, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
### There are prominent outliers for *distance* and *true price* variables, therefore, the dataset was transformed, setting the maximum values at the 99% percentile (35 miles and 600 EUR respectively).

@@

## 1.4.2 Distance

@@

## 1.4.3 Country
